A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}\censornotice

### 2020-01-29 2_related_work.tex
some more textual changes

% the context where our method can be positioned, and some related problems in that context
Under- and over-filling issues have a large proportional impact for thin geometric features.
\citeauthor{Jin2017a} proposed a sparse wavy path pattern for thin-walled parts~\cite{Jin2017a}.
Besides under- and over-filling, there are a few other robustness issues in toolpath generation for thin geometric features.
\citeauthor{Moesen2011} proposed a method to make beam compensation more reliable for thin geometric features~\cite{Moesen2011}.
\citeauthor{Behandish2019a} presented a method to characterize local- topological discrepancies due to material under- and over-deposition, and used this information to modify the as-manufactured outcomes~\cite{Behandish2019a}.

>>>>

% the context where our method can be positioned, and some related problems in that context
Under- and over-filling issues have a large proportional impact for thin geometric features.
\citeauthor{Jin2017a} proposed a sparse wavy path pattern for thin-walled parts~\cite{Jin2017a}.
Besides under- and over-filling, there are a few other robustness issues in toolpath generation for thin geometric features.
\citeauthor{Moesen2011} proposed a method to \revise{make beam compensation more reliable for}{reliably manufacture} thin geometric features\revise{}{ using laser-based additive manufacturing techniques}~\cite{Moesen2011}.
>> achange!!
\citeauthor{Behandish2019a} presented a method to characterize local- topological discrepancies due to material under- and over-deposition, and used this information to modify the as-manufactured outcomes~\cite{Behandish2019a}.

### 2020-01-29 6_2_printing_results.tex
some more textual changes

\subsubsection{Back pressure compensation}
We therefore keep the internal pressure constant, and vary the movement speed instead.
%In order to accurately realize a varying bead width we vary the movement speed, while keeping the internal pressure in the system constant.
One approach would be\revise{}{ to} keep the filament inflow $f$ (in \si{\milli\meter\cubed\per\second}) constant by varying movement speed accordingly \cite{Kuipers2018}.
However, that doesn't result in the intended filament outflow variation - see \cref{zero_back_pressure}.
We conjecture that the filament outflow is related to the total pressure in the system,
which depends not only on the amount of filament in between the feeder wheel and the nozzle (which we keep constant), 
but also depends on the back pressure that the previous layer exerts on the filament protruding from the nozzle.
The amount of back pressure is most likely monotonically related to the requested line width.
We compensate for the back pressure using a simple linear model:

>>>>

\subsubsection{Back pressure compensation}
Because changing the internal pressure is difficult in our setup,
we keep the internal pressure constant, and vary the movement speed instead.
%In order to accurately realize a varying bead width we vary the movement speed, while keeping the internal pressure in the system constant.
One approach would be\revise{}{ to} keep the filament inflow $f$ (in \si{\milli\meter\cubed\per\second}) constant by varying movement speed accordingly \cite{Kuipers2018}.
However, that doesn't result in the intended filament outflow variation - see \cref{zero_back_pressure}.
We conjecture that the filament outflow is related to the total pressure in the system,
which depends not only on the amount of filament in between the feeder wheel and the nozzle (which we keep constant), 
but also depends on the back pressure that the previous layer exerts on the filament protruding from the nozzle.
The amount of back pressure is most likely monotonically related to the requested line width.
We compensate for the back pressure using a simple linear model:
